Adaptive Approximation for Multivariate Linear Problems with Inputs Lying in a Cone

### 2019-08-17 DingHickKritzMakRICAMChapVerD.tex
Fix
Updates from Overleaf
testing

  \author[1]{Yuhan Ding}
  \author*[2]{Fred J. Hickernell}
  \author[3]{Peter Kritzer} 
  \author[4]{Simon Mak}
  \runningauthor{Y. Ding, F. J. Hickernell, P. Kritzer, and S. Mak}
  \affil[1]{Department of Mathematics, 
  Misericorida University, 301 Lake Street, Dallas, PA 18704 USA}
  \affil[2]{Department of Applied Mathematics, Illinois Institute of Technology, RE 220, 10 W.\ 32${}\text{nd}$ Street, Chicago, IL 60616 USA}
  \affil[3]{Johann Radon Institute for Computational and Applied Mathematics (RICAM), 
  Austrian Academy of Sciences, Altenbergerstr. 69, 4040 Linz, Austria}
  \affil[4]{Department of Statistical Science, Duke University, Durham, NC 27708-0251 USA}
  \title{Adaptive Approximation for Multivariate Linear Problems with Inputs Lying in a Cone}
  \runningtitle{Adaptive Approximation}
  %\subtitle{...}
  \abstract{We study adaptive approximation algorithms for general multivariate linear 
  problems where the sets of input functions are non-convex cones. While it is known that adaptive algorithms perform 
  essentially no better than non-adaptive algorithms for \DHKMchange{convex and symmetric} input sets, the 
  situation may be different for non-convex sets. A typical example
  considered here is function approximation based on series expansions. Given 
  an error tolerance, we use series coefficients of the input to construct an 
  approximate solution such that the error does not exceed this tolerance. We study the situation where we can bound the norm of the input based on a pilot sample, and the situation where we keep track of the decay rate of the series coefficients of the input. Moreover, 
  we consider situations where it makes sense to infer coordinate and smoothness importance. Besides performing an error analysis, we also study the information cost of our algorithms and the computational complexity 
  of our problems, and we identify conditions under which we can avoid a curse of 
  dimensionality.}
  %\keywords{...}
  %\classification[PACS]{...}
  %\communicated{...}
  %\dedication{...}
  %\received{...}
  %\accepted{...}
  %\journalname{...}
  %\journalyear{...}
  %\journalvolume{..}
  %\journalissue{..}
  \startpage{1}
  \aop
  %\DOI{...}

@@

Adaptive algorithms infer the necessary computational effort based on the function data sampled.  Adaptive algorithms may perform better than non-adaptive algorithms if the set of input functions is \emph{non-convex} \DHKMchange{or \emph{non-symmetric}}. \DHKMchange{Here we focus on the former situation and} construct adaptive algorithms for general multivariate linear problems where the input functions lie in non-convex cones. \DHKMchange{By a cone, we mean a set of functions where constant multiples of every element in the set also lie in the set. We study different variants of cone here, the precise definitions are given below.}

@@

We study the approximation of a linear solution operator $\SOL:\calF \to \calG$, which maps $f\in\calF$ to some $g\in\calG$, where we assume that $\calF$ and and $\calG$ are Banach spaces with norms $\norm[\calF]{\cdot}$ and $\norm[\calG]{\cdot}$, respectively. Our goal is to define a suitable set of input functions $\calC$, and an algorithm $\ALG(f,\varepsilon)$ for $f\in\calC$ that satisfies the error criterion
\begin{equation} \label{DHKM:err_crit}
    \norm[\calG]{\SOL(f) - \ALG(f,\varepsilon)} \le \varepsilon \qquad \forall \varepsilon > 0, \ f \in \calC,
\end{equation}
where  $\varepsilon$ denotes the error tolerance. Such an algorithm will  contain a rule for choosing $n$---depending on $f$ and $\varepsilon$.  The objectives of this chapter are to 
\begin{itemize}
    \item construct such a rule, 
    \item choose a set $\calC$ of input functions for which the rule is valid,  
    \item characterize the information cost of $\ALG$, 
    \item determine whether $\ALG$ has optimal information cost, and 
    \item understand the dependence of this cost on the number of input variables, $d$, as well as the error tolerance, $\varepsilon$.
\end{itemize}

We assume in this chapter that the functions $f\in\calF$ can be represented in terms of a basis representation as $f = \sum_{\bsk \in \mathbb{K}} \hf(\bsk) u_{\bsk}$, and we allow algorithms $\ALG (f,\varepsilon)$ to use $n=n(f,\varepsilon)$ coefficients $\hf (\bsk)$ of this representation. That is, 
we study algorithms that have an output of the form 
\begin{equation*} 
  \sum_{i=1}^{n(f,\varepsilon)}\hf(\bsk_i) u_{\bsk_i} \qquad \forall f \in \calF, \ n \in \N,
\end{equation*}
where an oracle provides $\hf(\bsk_1),\ldots,\hf (\bsk_{n(f,\varepsilon)})$ 
with $n(f,\varepsilon)$ being chosen based on a stopping rule. 
We assume that it is possible to sample the series coefficients of the input function.  This is a \DHKMchange{more} restrictive assumption than being able to sample any linear functional, but it is \DHKMchange{less} restrictive than only being able to sample function values.  An important future problem is to extend the theory in this chapter to the case where the only function data available are function values.

The information cost of $\ALG(f,\varepsilon)$ is denoted $\COST(\ALG,f,\varepsilon)$ and defined as the number of function data---in our situation, series coefficients---required by $\ALG(f,\varepsilon)$.  For adaptive algorithms this cost varies with the input function $f$.  We call an algorithm \emph{non-adaptive} if $n(f,\varepsilon)=n(\varepsilon)$, independently of the particular choice of $f\in\calC$.

@@

We demonstrate below that non-adaptive algorithms are optimal when the set of inputs is chosen to be $\calC = \calB_R$. However, typically one cannot bound the norm of the input function a priori, so non-adaptive algorithms may be impractical. 
This will lead to \emph{adaptive} algorithms $\ALG$ satisfying error criterion \eqref{DHKM:err_crit}.  For such algorithms, the set of allowable input functions, $\calC$, will be a \emph{cone}, not a ball. By a cone, we mean a set of functions where the constant multiples of each element of the set also lie in the set. We study different variants of cones in different sections of this chapter. The first definition of a cone is given in \eqref{DHKM:pilot_cone}, 
where the idea is that the consists of $f\in\calF$ such that 
$$
  \norm[\calF]{f}\le h (\hf(\bsk_1),\ldots,\hf (\bsk_{n_1}))
$$
for a suitably chosen homogeneous function $h:\bbR\to [0,\infty)$. This means that the norm of $f$ can be bounded well in terms of 
a \emph{pilot sample} of size $n_1\in\bbN$. See \eqref{DHKM:pilot_cone} for the precise definition. In Section \ref{DHKM:SecAdapAlgTrackDecay}, we will modify the definition of cones such that we can keep track of the decay rate of the series coefficients of the input function (see \eqref{DHKM:TrackConeDef}), 
and in Section \ref{DHKM:smoothimportance_sec} we allow a situation 
where we infer coordinate and smoothness importance from some initial data, thus making the definition of the cone more practical (see  
\eqref{DHKM:pilot_cone2}).

@@

Section \ref{DHKM:smoothimportance_sec} considers the case where the most suitable weights $\bslambda$ are not known a priori and are instead inferred from function data.  Adaptive Algorithm \ref{DHKM:InfPilotConeAlg} combines this inference step with Algorithm \ref{DHKM:PilotConeAlg} to construct an approximation that satisfies the error criterion.

@@

\section{General Setting}\label{DHKM:secprobdef}

\PeterNote{Can we find a better heading for this section?}
\FredNote{How about the above?}

@@

The error of this approximation in terms of the norm on the output space, $\calG$, can be expressed as
\begin{gather*}
    \norm[\calG]{\SOL(f) - \APP(f,n)} = \norm[2]{\bigl(\hf(\bsk_i) \bigr)_{i=n+1}^{\infty}}, \\
    \text{where}\qquad
    \norm[\calG]{\sum_{\bsk \in \N_0^d} \hg(\bsk) u_{\bsk}} : = \norm[2]{\bigl(\hg(\bsk) \bigr)_{\bsk \in \N_0^d}}.
\end{gather*}
If one has a fixed data budget, $n$, then $\APP(f,n)$ is the best answer \DHKMchange{for certain classes of inputs in $\calF$ as for example balls, which 
are among the most prominent examples studied in the literature}.

@@

\begin{lemma} \label{DHKM:NoNonAdpatLem}
For a given set of input functions, $\calC$, if  $\calA(\calC)$ contains any non-adaptive algorithms, then for every $\varepsilon > 0$,
\begin{equation*}
    \COMP(\calA(\calC),\varepsilon) : = \sup_{R > 0} \COMP(\calA(\calC),\varepsilon, R) < \infty.
\end{equation*}
\end{lemma}

@@

\DHKMchange{Accordingly, we now define the cone of functions whose norm can be bounded well in terms of a pilot sample, $\{\hf(\bsk_1), \ldots, \hf(\bsk_{n_1})\}$. It is given by}
\begin{equation} \label{DHKM:pilot_cone}
    \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} = \left \{ f \in \calF : \norm[\calF]{f} \le A \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \right\}.
\end{equation}
Referring to error bound \eqref{DHKM:Refined_APP_err}, we see that the error of $\APP(f,n)$ depends on the series coefficients not sampled.  The definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ allows us to bound these as follows: 
\begin{align*}
     \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty} & =  \left[ \norm[\calF]{f}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
    \right]^{1/\rho} \qquad \forall f \in \calF \\
    &  \le  \left[ A^\rho \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
    \right]^{1/\rho} \quad \forall f \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}.
\end{align*}
This inequality together with error bound \eqref{DHKM:Refined_APP_err} implies the data-based error bound 
\begin{subequations} \label{DHKM:pilot_errbd}
\begin{equation}
\norm[\calG]{\SOL(f) - \APP(f,n)}  \le \ERRN  \qquad \forall f \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}},
\end{equation}
where 
\begin{multline}
\ERRN \\
    : =  
    \left[ A^\rho \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho \right]^{1/\rho} 
    \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} , 
    \\ n \ge n_1.
\end{multline}
\end{subequations}
This error bound decays as $\bignorm[\rho]{\bigl( f(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^n}$ increases and as the tail norm of the $\lambda_{\bsk_i}$ decreases.  This data-driven error bound underlies  Algorithm \ref{DHKM:PilotConeAlg}, which is successful for $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ defined in \eqref{DHKM:pilot_cone}:

@@

Now, construct the input function $f_2$, having zero coefficients for $\bsk \in \calJ$ and also as in Lemma \ref{DHKM:Key_Lem}:
\begin{gather}
\nonumber
    \bigabs{\hf_2(\bsk)} = \begin{cases} \displaystyle \frac{R (1-1/A) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}^{\rho'/\rho}}, &  \bsk \notin \calJ, \\
    0, & \bsk \in \calJ, 
    \end{cases}
    \qquad \norm[\calF]{f_2} = \frac{R(1 - 1/A)}{2}, \\
    \label{DHKM:SOLf2bd}
    \norm[\calG]{\SOL(f_2)} = \frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}.
\end{gather}
Let $f_{\pm} = f_1 \pm f_2$.  By the definitions above, it follows that
\begin{align}
\nonumber
    \norm[\calF]{f_{\pm}} &= \norm[\calF]{ f_1 \pm f_2 } \le \norm[\calF]{ f_1} + \norm[\calF]{ f_2 } =  R, \\
    \nonumber
    \norm[\rho]{\left( \frac{\hf_\pm(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} 
    & = \norm[\rho]{\left( \frac{\hf_1(\bsk_i) \pm \hf_2(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \\
    \nonumber
    & \ge \norm[\rho]{\left( \frac{\hf_1(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} - \norm[\rho]{\left( \frac{\hf_2(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \\
    \nonumber
    & \ge \norm[\calF]{ f_1} - \norm[\calF]{ f_2 } =  \frac{R}{A} \ge \frac{\norm[\calF]{f_{\pm}}}{A}.
\end{align}
Therefore, $f_\pm \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} \cap \calB_R$.  Moreover, since the series coefficients for $f_\pm$ are the same for $\bsk \in \calJ$, it follows that $\ALG'(f_+,\varepsilon) = \ALG'(f_-,\varepsilon)$.  Thus, $\SOL(f_{+})$ must be quite similar to $\SOL(f_{-})$.

@@

We may not be able to guarantee that a particular $f$ of interest lies in our cone, $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$, but we may derive necessary conditions for $f$ to lie in $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$.  The following proposition follows from the definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ in \eqref{DHKM:pilot_cone} and the fact that the term on the left below underestimates $\norm[\calF]{f}$.

\YuhanNote{Should we delete Proposition 1 just keep Propostion 2?}
\begin{proposition}
If $f \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$, then 
\begin{equation} \label{DHKM:PilotConeNecessary}
    \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{\DHKMchange{i =1}}^{n}} \le A
    \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \qquad \forall n \in \NN.
\end{equation}
\end{proposition}

@@

\DHKMchange{Let's consider an alternative cone, i.e.,
\[\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}=\{ f \in \calF : \norm[\calF]{f} \le A'\norm[\calF']{f}\},\]
where
$\norm[\calF']{f} =\norm[\rho]{\left( \frac{\hf(\bsk)\omega_{\bsk}}{\lambda_{\bsk}} \right)_{\bsk \in \mathbb{K}}}$ and $\omega_{\bsk}$ decreases. 
\begin{proposition}
If there exists $A,A',A'', n_1,$ and $\boldsymbol{\omega}$ such that
\[\omega_{n_1} A'' \ge A \ge \omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho} \text{ and} \qquad  \omega_{n_1+1}A' < 1, \]
then 
\[\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}
\subseteq 
\calC_{\boldsymbol{\lambda}, A}
\subseteq
\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}.\]
\end{proposition}

>>>>

  \author[1]{Yuhan Ding}
  \author*[2]{Fred J. Hickernell}
  \author[3]{Peter Kritzer} 
  \author[4]{Simon Mak}
  \runningauthor{Y. Ding, F. J. Hickernell, P. Kritzer, and S. Mak}
  \affil[1]{Department of Mathematics, 
  Misericorida University, 301 Lake Street, Dallas, PA 18704 USA}
  \affil[2]{Department of Applied Mathematics, Illinois Institute of Technology, RE 220, 10 W.\ 32${}\text{nd}$ Street, Chicago, IL 60616 USA}
  \affil[3]{Johann Radon Institute for Computational and Applied Mathematics (RICAM), 
  Austrian Academy of Sciences, Altenbergerstr. 69, 4040 Linz, Austria}
  \affil[4]{Department of Statistical Science, Duke University, Durham, NC 27708-0251 USA}
  \title{Adaptive Approximation for Multivariate Linear Problems with Inputs Lying in a Cone}
  \runningtitle{Adaptive Approximation}
  %\subtitle{...}
  \abstract{We study adaptive approximation algorithms for general multivariate linear 
  problems where the sets of input functions are non-convex cones. While it is known that adaptive algorithms perform 
  essentially no better than non-adaptive algorithms for \DHKMchange{convex and symmetric} input sets, the 
  situation may be different for non-convex sets. \DHKMchange{The setting} 
  considered here is function approximation based on series expansions. Given 
  an error tolerance, we use series coefficients of the input to construct an 
  approximate solution such that the error does not exceed this tolerance. We study the situation where we can bound the norm of the input based on a pilot sample, and the situation where we keep track of the decay rate of the series coefficients of the input. Moreover, 
  we consider situations where it makes sense to infer coordinate and smoothness importance. Besides performing an error analysis, we also \DHKMchange{derive upper bounds on} the information cost of our algorithms and \DHKMchange{lower bounds on} the computational complexity 
  of our problems, and we identify conditions under which we can avoid a curse of 
  dimensionality.}
  %\keywords{...}
  %\classification[PACS]{...}
  %\communicated{...}
  %\dedication{...}
  %\received{...}
  %\accepted{...}
  %\journalname{...}
  %\journalyear{...}
  %\journalvolume{..}
  %\journalissue{..}
  \startpage{1}
  \aop
  %\DOI{...}

@@

Adaptive algorithms infer the necessary computational effort based on the function data sampled.  Adaptive algorithms may perform better than non-adaptive algorithms if the set of input functions is \emph{non-convex} \DHKMchange{or \emph{non-symmetric}}. \DHKMchange{Here we focus on the former situation and} construct adaptive algorithms for general multivariate linear problems where the input functions lie in non-convex cones. \DHKMchange{By a cone, we mean a set of functions where constant multiples of every function in the set also lie in the set. The precise definitions of the cones that we study are given below.}

@@

We study the approximation of a linear solution operator $\SOL:\calF \to \calG$, which maps $f\in\calF$ to some $g\in\calG$, where we assume that $\calF$ and and $\calG$ are Banach spaces with norms $\norm[\calF]{\cdot}$ and $\norm[\calG]{\cdot}$, respectively. Our goal is to define a suitable set of input functions $\calC$, and an algorithm $\ALG(\cdot,\cdot):\calC \times (0,\infty) \to \calG$ that satisfies the error criterion:
\begin{equation} \label{DHKM:err_crit}
    \norm[\calG]{\SOL(f) - \ALG(f,\varepsilon)} \le \varepsilon \qquad \forall \varepsilon > 0, \ f \in \calC,
\end{equation}
where  $\varepsilon$ denotes the error tolerance. Such an algorithm will  contain a rule for choosing the number of series coefficients required, $n(f,\varepsilon)$, which depends on $f$ and $\varepsilon$.  The objectives of this chapter are to 
\begin{itemize}
    \item construct such a rule, 
    \item choose a set $\calC$ of input functions for which the rule is valid,  
    \item characterize the information cost of $\ALG$, 
    \item determine whether $\ALG$ has optimal information cost, and 
    \item understand the dependence of this cost on the number of input variables, $d$, as well as the error tolerance, $\varepsilon$.
\end{itemize}

We assume in this chapter that the functions $f\in\calF$ can be represented in terms of a basis representation as $f = \sum_{\bsk \in \mathbb{K}} \hf(\bsk) u_{\bsk}$, and we allow algorithms $\ALG (f,\varepsilon)$ to use $n=n(f,\varepsilon)$ coefficients $\hf (\bsk)$ of this representation. That is, 
we study algorithms that have an output of the form 
\begin{equation*} 
  \ALG(f,\varepsilon) = \sum_{i=1}^{n(f,\varepsilon)}\hf(\bsk_i) u_{\bsk_i} \qquad \forall f \in \calF, \ n \in \N,
\end{equation*}
where an oracle provides $\hf(\bsk_1),\ldots,\hf (\bsk_{n(f,\varepsilon)})$ 
with $n(f,\varepsilon)$ being chosen based on a stopping rule. 
We assume that it is possible to sample the series coefficients of the input function.  This is a \DHKMchange{more} restrictive assumption than being able to sample any linear functional, but it is \DHKMchange{less} restrictive than only being able to sample function values.  An important future problem is to extend the theory in this chapter to the case where the only function data available are function values.

The information cost of $\ALG(f,\varepsilon)$ is denoted $\COST(\ALG,f,\varepsilon)$ and defined as the number of function data---in our situation, series coefficients---required by $\ALG(f,\varepsilon)$, i.e., $\COST(\ALG,f,\varepsilon) = n(f,\varepsilon)$.  For adaptive algorithms this cost varies with the input function $f$.  We call an algorithm \emph{non-adaptive} if $n(f,\varepsilon)=n(\varepsilon)$, independently of the particular choice of $f\in\calC$.

@@

We demonstrate below that non-adaptive algorithms are optimal when the set of inputs is chosen to be $\calC = \calB_R$. However, typically one cannot bound the norm of the input function a priori, so non-adaptive algorithms may be impractical. 
This will lead to \emph{adaptive} algorithms $\ALG$ satisfying error criterion \eqref{DHKM:err_crit}.  For such algorithms, the set of allowable input functions, $\calC$, will be a \emph{cone}, not a ball. We study different variants of cones in different sections of this chapter. The first definition of a cone is given in \eqref{DHKM:pilot_cone}, 
where the idea is that the cone consists of $f\in\calF$ such that 
$$
  \norm[\calF]{f}\le h (\hf(\bsk_1),\ldots,\hf (\bsk_{n_1}))
$$
for a suitably chosen homogeneous function $h:\bbR\to [0,\infty)$. This means that the norm of $f$ can be bounded well in terms of 
a \emph{pilot sample} of size $n_1\in\bbN$. See \eqref{DHKM:pilot_cone} for the precise definition. In Section \ref{DHKM:SecAdapAlgTrackDecay}, we will modify the definition of cones such that we can keep track of the decay rate of the series coefficients of the input function (see \eqref{DHKM:TrackConeDef}), 
and in Section \ref{DHKM:smoothimportance_sec} we allow a situation 
where we infer coordinate and smoothness importance from some initial data, thus making the definition of the cone more practical (see  
\eqref{DHKM:pilot_cone2}).

@@

Section \ref{DHKM:smoothimportance_sec} considers the case where the most suitable weights $\bslambda$, which are used to define the input space, are not known a priori and are instead inferred from function data.  Adaptive Algorithm \ref{DHKM:InfPilotConeAlg} combines this inference step with Algorithm \ref{DHKM:PilotConeAlg} to construct an approximation that satisfies the error criterion.

@@

\section{Formal Setting}\label{DHKM:secprobdef}

@@

The error of this approximation in terms of the norm on the output space, $\calG$, can be expressed as
\begin{gather*}
    \norm[\calG]{\SOL(f) - \APP(f,n)} = \norm[2]{\bigl(\hf(\bsk_i) \bigr)_{i=n+1}^{\infty}}, \\
    \text{where}\qquad
    \norm[\calG]{\sum_{\bsk \in \N_0^d} \hg(\bsk) u_{\bsk}} : = \norm[2]{\bigl(\hg(\bsk) \bigr)_{\bsk \in \N_0^d}}.
\end{gather*}
Here we have chosen $\tau = 2$ so $\rho'=\infty$.  If one has a fixed data budget, $n$, then $\APP(f,n)$ is the best answer \DHKMchange{for certain classes of inputs in $\calF$ as for example balls, which 
are among the most prominent examples studied in the literature}.

@@

\begin{lemma} \label{DHKM:NoNonAdpatLem}
For a given set of input functions, $\calC$, if  $\calA(\calC)$ contains any non-adaptive algorithms, then for every $\varepsilon > 0$,
\begin{equation*}
    \COMP(\calA(\calC),\varepsilon) : = \sup_{R > 0} \COMP(\calA(\calC),\varepsilon, R) < \infty.
\end{equation*}
\end{lemma}
}

@@

\DHKMchange{Accordingly, we now define the cone of functions whose norm can be bounded well in terms of a pilot sample, $\{\hf(\bsk_1), \ldots, \hf(\bsk_{n_1})\}$. It is given by}
\begin{equation} \label{DHKM:pilot_cone}
    \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} = \left \{ f \in \calF : \norm[\calF]{f} \le A \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \right\}.
\end{equation}
Referring to error bound \eqref{DHKM:Refined_APP_err}, we see that the error of $\APP(f,n)$ depends on the series coefficients not sampled.  The definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ allows us to bound these as follows: 
\begin{align*}
     \MoveEqLeft{\norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}} \\
     & =  \left[ \norm[\calF]{f}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
    \right]^{1/\rho} \qquad \forall f \in \calF \\
    &  \le  \left[ A^\rho \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
    \right]^{1/\rho} \quad \forall f \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}.
\end{align*}
This inequality together with error bound \eqref{DHKM:Refined_APP_err} implies the data-based error bound 
\begin{subequations} \label{DHKM:pilot_errbd}
\begin{equation}
\norm[\calG]{\SOL(f) - \APP(f,n)}  \le \ERRN  \qquad \forall f \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}},
\end{equation}
where 
\begin{multline} \label{ErrNDef}
\ERRN \\
    : =  
    \left[ A^\rho \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho \right]^{1/\rho} 
    \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} , 
    \\ \forall n \ge n_1.
\end{multline}
\end{subequations}
This error bound decays as $\bignorm[\rho]{\bigl( f(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^n}$ increases and as the tail norm of the $\lambda_{\bsk_i}$ decreases.  This data-driven error bound underlies  Algorithm \ref{DHKM:PilotConeAlg}, which is successful for $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ defined in \eqref{DHKM:pilot_cone}:

@@

Now, construct the input function $f_2$, having zero coefficients for $\bsk \in \calJ$ and also as in Lemma \ref{DHKM:Key_Lem}:
\begin{gather}
\nonumber
    \bigabs{\hf_2(\bsk)} = \begin{cases} \displaystyle \frac{R (1-1/A) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}^{\rho'/\rho}}, &  \bsk \notin \calJ, \\
    0, & \bsk \in \calJ, 
    \end{cases}
    \qquad \norm[\calF]{f_2} = \frac{R(1 - 1/A)}{2}, \\
    \label{DHKM:SOLf2bd}
    \norm[\calG]{\SOL(f_2)} = \frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}.
\end{gather}

Let $f_{\pm} = f_1 \pm f_2$.  By the definitions above, it follows that
\begin{align}
\nonumber
    \norm[\calF]{f_{\pm}} &= \norm[\calF]{ f_1 \pm f_2 } \le \norm[\calF]{ f_1} + \norm[\calF]{ f_2 } =  R, \\
    \nonumber
    \norm[\rho]{\left( \frac{\hf_\pm(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} 
    & = \norm[\rho]{\left( \frac{\hf_1(\bsk_i) \pm \hf_2(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \\
    \nonumber
    & \ge \norm[\rho]{\left( \frac{\hf_1(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} - \norm[\rho]{\left( \frac{\hf_2(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \\
    \nonumber
    & \ge \norm[\calF]{ f_1} - \norm[\calF]{ f_2 } =  \frac{R}{A} \ge \frac{\norm[\calF]{f_{\pm}}}{A}.
\end{align}
Therefore, $f_\pm \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} \cap \calB_R$.  Moreover, since the series coefficients for $f_\pm$ are the same for $\bsk \in \calJ$, it follows that $\ALG'(f_+,\varepsilon) = \ALG'(f_-,\varepsilon)$.  Thus, $\SOL(f_{+})$ must be quite similar to $\SOL(f_{-})$.

@@

\DHKMchange{We may not be able to guarantee that a particular $f$ of interest lies in our cone, $\calC_{\boldsymbol{\lambda},n_1,A}$, but the definition of $\ERRN$ in \eqref{ErrNDef} provides a necessary condition for  $f$ to lie in $\calC_{\boldsymbol{\lambda},n_1,A}$, namely,
\begin{equation} \label{DHKM:PilotConeNecessary}
    \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{\DHKMchange{i =1}}^{n}} \le A
    \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \qquad \forall n \in \NN.
\end{equation}
}

@@

\DHKMchange{Let's consider an alternative cone, i.e.,
\begin{equation} \label{DHKM:altconedef}
    \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}=\{ f \in \calF : \norm[\calF]{f} \le A'\norm[\calF']{f}\},
\end{equation}
where
$\norm[\calF']{f} =\norm[\rho]{\left( \frac{\hf(\bsk)\omega_{\bsk}}{\lambda_{\bsk}} \right)_{\bsk \in \mathbb{K}}}$ and $\omega_{\bsk}$ decreases. The norm $\norm[\calF']{\cdot}$ is weaker than the norm $\norm[\calF]{\cdot}$, so this cone is defined as the subset of $\calF$ for which the weaker norm of the function  provides an upper bound the stronger norm of the function.  The following proposition describes the relationship between the cones defined in \eqref{DHKM:pilot_cone} and \eqref{DHKM:altconedef}.
\begin{proposition}
If there exists $A,A',A'', n_1,$ and $\boldsymbol{\omega}$ such that
\[\omega_{n_1} A'' \ge A \ge \omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho} \text{ and} \qquad  \omega_{n_1+1}A' < 1, \]
then 
\[\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}
\subseteq 
\calC_{\boldsymbol{\lambda}, A}
\subseteq
\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}.\]
\end{proposition}
